Approximation as Differentiation

### 2025-03-31 notes/sec/some-categories-with-biproducts.tex
Onto vector space over a field F.

>>>>

\begin{definition}[Vector space over a field $F$]
Suppose $F$ a field with addition of elements written $a + b$ and multiplication written $a \mult b$.
Overloading $+$ and $\mult$, define a \emph{vector space $V = (V, +, \mult)$ over $F$} to be a set $V$
equipped with addition of vectors $+: V^2 \to V$ () and scalar multiplication $\mult: F \times V \to V$ where
$(V,+)$ is an Abelian group and the vector operations are compatible with the field operations in that the
following equations hold:
\begin{itemize}
\item $0 + a = a$
\item $1 \mult a = a$
\item $(a \mult b) \mult v = a \mult (b \mult v)$
\item $(a + b) \mult v = (a \mult v) + (b \mult v)$
\item $a \mult (u + v) = (a \mult u) + (b \mult v)$
\end{itemize}
\end{definition}
